---
title: "Laura K. Hilton, PhD"
subtitle: "Curriculum Vitae"

# Use the multibib extension
filters:
  - multibib

# Turn off YAML validation
validate-yaml: false

# Define list of separate bibliography files
bibliography:
  talks: references/talks.bib
  posters: references/posters.bib
  papers: references/papers.bib
  not-reviewed: references/not-peer-reviewed.bib
nocite: |
    @*

# Disable citeproc
citeproc: false

# Custom cross reference type for appendix tables
crossref:
  custom:
    - kind: float
      key: apptbl
      latex-env: apptbl
      reference-prefix: Table A
      space-before-numbering: false
      latex-list-of-description: Appendix Table
apptbl-cap-location: top


---

```{r}
#| label: setup

library(tidyverse)
library(kableExtra)

```

# Education

# Appointments

# Awards and Honours

## Publications

```{r}
#| label: count-citations

# Read the file content into a single string
text_content <- readLines("references/papers.bib", warn = FALSE)
text_content <- paste(text_content, collapse = "\n")

# Count the occurrences of a pattern
pattern <- "@"
count <- str_count(text_content, pattern)

```

## Published Peer-Reviewed Articles and Preprints
*`r count` total; 12 as co-first author*

## Invited Commentary

# Presentations

## Invited Presentations



## Conference Oral Presentations

::: {#refs-talks}
:::

\newpage


## Conference Poster Presentations


::: {#refs-posters}
:::

\newpage

# Career Disruptions

# Service

## Anonymous Peer Review (2018-Present, Cumulative)

ASH Annual Meeting Abstracts (1), Blood (7), Haematologica (3), Journal of Clinical Oncology (3), Genome Medicine (1), Nature Communications (1), Blood Advances (8), Journal of Molecular Diagnostics (1), Cell Genomics (1). 

## Service to University and Community